On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-04-30 paper_lap/JCP_response1/response.tex

\documentclass[11pt]{letter}
\usepackage{amsmath,amsthm,amssymb,amscd}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{comment}
\usepackage{mathpazo}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}

@@

\qa
5) p. 13. I find the choice of notation in Theorem 8 to be very poor. In particular $A_{0}$ and $f_{0}$ are
used right above in (56) to denote the local problem after the corner has been refined ($A_{0}$ is of size
$P + 2M \times P + 2M$). Then in the statement of the theorem, these variables are used to denote the
analogous variables on just the corner panel of the unrefined problem ($A_{0}$ is of size $P \times P$ ), and then
in the proof of the result these variables are used to refer to the original corner panel as well as the
adjacent panels ($A_{0}$ is of size $P + 2M \times P + 2M$ ). Also, I am not sure why $f_{0}$ is not underlined, since it is a vector. Could you please fix this notation?

\qb
\todo{JH}

\qa
6) p. 19. In the same vein as comment 3, I find the absence of any information on conditioning to be a bit startling, since one of the main appeals of working with boundary integral equations is the ability
to form well-conditioned discretizations. Again, I am aware that this falls squarely into the scope of existing work (again, probably [14]), but find this also sufficiently important to at least summarize in the current work.

\qb
We have included a remark to point out that the conditioning for the solution of Neumann problem is inherited from its corresponding Dirichlet discretization. (see remark)

As noted, with our approach, the conditioning of the discrete system for the Neumann problem inherits the properties of the corresponding Dirichlet discretization. The conditioning of using this approach as expected is independent of the number of points used in the discretization. However, the physical conditioning of the problem itself is fairly complicated owing to the presence of continuous spectra on various intervals whose sizes depend on the angles formed at the corners. This is reflected in any Dirichlet or Neumann discretization for regions with corners and falls outside the scope of this work. For the triangle example, we have included a plot of the spectrum of the operator here for reference. We also plot the spectrum of the discretized operator based on a dyadic mesh at the corner.
\begin{center}
\includegraphics[width=0.4\linewidth]{sp-eigs-plot.pdf}
\includegraphics[width=0.4\linewidth]{ref-eigs-plot.pdf}
\end{center}

Similar plots for the singular values of the operators for Dirichlet problem for Laplace and Stokes equations have already been reported in [1] and we feel that it would take away from the main point of the paper.

1. K.~Serkh, V.~Rokhlin, On the solution of elliptic partial differential
  equations on regions with corners, Journal of Computational Physics 305
  (2016) 150--171.

\qa
7) p. 19. Even for a problem with 22k dofs, 105 iterations of a Krylov method seems like a lot, especially if the problem is well-conditioned. I can't help but wonder if this is an artifact of the fact that your FMM tolerance is the same as your iterative method tolerance. If you set the latter to 1e-14 or 1e-13, does the number of iterations decrease drastically?

\qb
We use a version of GMRES which does not suffer from stagnation at low thresholds and an FMM whose tolerance was set to $5 \times 10^{-16}$. The number of iterations do not reduce drastically if we increase the iteration count. We attach here a plot of the relative residual as a function of iteration number. 
\begin{center}
\includegraphics[width=0.7\linewidth]{lap-iter-count-wheel.pdf}
\end{center}

Our boundary data has randomly generated charge strengths and sources. For a new run, the original discretization requires $106$ iterations for the Neumann problem. The iteration count for the corresponding adjoint Dirichlet problem is $83$, and iteration count on doubling the number of points in our existing discretization is $106$.

@@

\qa
8) 
p. 21-22. I find the content of Appendix B difficult to understand for a number of reasons. The motivation for such a result is clear, but I'm not sure I totally understand the conclusion. In particular, you want to show that using the adjoint discretization one can interpolate the density on a panel far from the corner. That makes sense. Your approach to showing this is to use the relation (B.1) to find another equivalent integral equation, which you then show can be solved using existing information accurately.
Is the claim that to actually interpolate the density on such a panel, one would need to solve another Dirichlet problem, and it does NOT suffice to just interpolate the value of $\sigma$ obtained on the GL nodes when solving the original problem? Please clarify this point.

There are these other issues I?m having with it:
(a) On your assumptions about the discretization, 1 and 3 have an easy-to-understand interpretation. It's unclear to me what 2 is really assuming about the discretization, given that it seems to mostly to be introducing notation. Of course, I can imagine conditions where $\rho_{0}$ is less than the width of some panels, but is there some deeper restriction?
(b) Your assumption that $\rho_{0}>1$ and your later statement that the rate at which a polynomial interpolant will converge is $C \rho_{0}^{M}$ is a bit awkward, since these choices are specific for a function
on an interval of length 2.
(c) The second paragraph on p. 22 is very unclear to me. I don?t even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as $\gamma([s1,s2])$, or what is really even meant by ?segment? here. Furthermore, it is mentioned that k(s, t) when considered as a function of $t \in \mathbb{C}$ has a singularity at $\gamma(s)$. Given the current setup wouldn't the singularity be at s? I would recommend rewriting this entire paragraph to be more transparent.

\qb
Thank you for bringing this to our notice. The section as written was confusing and we have rewritten the section completely to address all of the concerns above and feel that the readability now is significantly improved. We have eliminated the assumptions on the geometry completely as it can be confusing and rather reduced it to an error estimate of a solution to a Dirichlet problem using the same grid. The purpose of our approach is to show that a good Dirichlet discretization of the corner problem can be reutilized to obtain a discretization of the Neumann problem.
\qa
Small fixes and typos:

@@

\qb
\todo{JH}

\qa
Reviewer \#4:
This article is not suitable for JCP. Most of it is Theorem, Lemma, Proposition, Remark. Journal of Computational Physics focuses on computational aspects of physical problems and contributions in mathematical and numerical modeling, rather than numerical analysis. This paper should be submitted to SIAM NUM ANALYS., or IMA J. NUM. ANAL., or Numerische Mathematik.

\qb
The solution of Laplace's equation in complicated domains is a classical problem in computational physics and has a large array of applications such as electrostatics, fluid flow, diffusion, and magnetohydrodynamics to name a few.  The use of theorems, lemmas, propositions has been mainly to summarize existing work based which serves as a foundation for our method. Here are a few other examples of papers in JCP which we believe are written in a similar style.

@@

\qa

The scope of the article completely misses an entire arena of literature in the field, the unified transform (Fokas) method that has attacked the problem at hand in a much cleaner and nicer way in only 12 lines of code. It does not require a discretization with 22,240 points. See the work by Dr. Anthony Charles Lewis Ashton, Matthew J. Colbrook, and Natasha Flyer.

\qb

The unified transform method while handles the solution of Laplace's equation on simple polygons, it does not scale for larger problems like the ones presented in the paper. The "broken wheel" region for which $22,240$ nodes have been used has $107$
corners and edges, thereby just requiring approximately $200$ nodes per edge for discretization. Moreover, our method has been coupled to FMMs thereby able to solve this problems in $O(N)$ CPU time, where $N$ is the number of degrees of freedom required to discretize the problem. We believe that Fokas' method wouldn't be competitive as compared to our method (105 iterations in 15 secs to 13 digits of accuracy and plotting the solution at 250000 points in 6.5 secs on a single CPU core).
Moreover, our method also extends to discretizations of the Helmholtz problem (for any complex wave number in the first quadrant) and we are currently in the process of describing the discretization procedure for both Dirichlet and Neumann boundary value problems. 
\qa

@@

The method does the simplest of problems, Laplace on a convex domain, that was attacked much earlier and neater in 2001/2003 by Fokas. This paper does not show non-convex polygonal domains or Helmholtz or modified Helmholtz.

\qb

As stated above, the approach does not scale well for large complicated problems. Moreover, our example for the solution in the exterior of the "broken wheel" geometry is emphatically non-convex and we believe is suitably complicated as well.

We thank the reviewer for their careful reads of our manuscript, and comments 
which have helped significantly improve the quality of the manuscript.
We hope that our revised manuscript based on their suggestions is now
suitable for publication in JCP-X.

### 2020-04-30 paper_lap/JCP_response1/05apparatus.tex
updating response

\begin{remark1}
\label{rem:far-field-accuracy}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark1}
\begin{remark1}
\label{rem:strong-sol-smooth}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark1}

>>>>

\begin{remark}
\label{rem:far-field-accuracy}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark}
\begin{remark}
\label{rem:strong-sol-smooth}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark}
\begin{remark}
In this approach, note that the discretization of the Neumann problem, inherits its spectral properties from the discretization of the corresponding adjoint Dirichlet problem (eigenvalues and singular values are the same, but eigenvectors and singular vectors may differ). Thus, when using an iterative method for solving the discrete linear system for the Dirichlet and Neumann problem, the number of iterations required for the relative residual to converge below $\varepsilon$ would be fairly similar. 
\end{remark}

### 2020-04-30 paper_lap/JCP_response1/manuscript.tex
updating response

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
{\color{blue}
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$ and the corresponding weights are given by $w_{1}, \ldots w_{N}$.
Let $X = \mathbb{L}^2({\Gamma})$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.
Let $S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.}

\note{Is there a clean way to give an explicit definition of P or it's obvious?}

{\color{blue}
Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential. Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution.   Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$. Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
\begin{equation}
e = \max_{i=1,2\ldots M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
\end{equation}

@@

\note{Do we include a description of the discretization procedure we use in practice?}

>>>>

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
{\color{blue}
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$ and the corresponding weights are given by $w_{1}, \ldots w_{N}$.
Let $X = \mathbb{L}^2({\Gamma})$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.
Let $S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.

Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential. Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution.   Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$. Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
\begin{equation}
e = \max_{i=1,2\ldots M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
\end{equation}

@@
